---
title: "partition"
output: pdf_document
date: "2024-03-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, set.seed("611"))
```

# Partition simple

```{r}
#setwd("~/Repositories/cherry-stats/projets/LAL")
load("qaly.RData")
library(dplyr)
library(boot)
library(survRM2)
```

```{r conversion}
qaly$finctdt   <- apply(qaly[,c("C1dt","C2dt" , "C3dt" , "C4dt", "Inter1dt" )],1,max,na.rm=T)
qaly$finct.dt <- as.Date(as.character(qaly$finctdt),format="%Y-%m-%d")

```

```{r calcul delais}
qaly$suivi  <- as.numeric(qaly$Datemax-qaly$randodt)/(365.25/12)
qaly$survie <- as.numeric(qaly$deathdt-qaly$randodt)/(365.25/12)
qaly$delfinct <- as.numeric(qaly$finct.dt-qaly$randodt)/(365.25/12)
qaly$delarr <- as.numeric(qaly$arrpremadt-qaly$randodt)/(365.25/12)
qaly$delfinct[which(qaly$delfinct==0)]<- qaly$delarr[which(qaly$delfinct==0)]
qaly$finct<- rep(1,length(qaly$delfinct))
qaly$delrec<- as.numeric(qaly$relapsdt-qaly$randodt)/(365.25/12)
qaly$delpfs<- qaly$suivi
qaly$delpfs[!is.na(qaly$delrec)]<-qaly$delrec[!is.na(qaly$delrec)]
qaly$delbmt <- as.numeric(qaly$bmtdt-qaly$randodt)/(365.25/12)
qaly$delbmt1 <- as.numeric(qaly$cgvhdt-qaly$randodt)/(365.25/12)
qaly$delbmt2 <- as.numeric(qaly$agvhdt-qaly$randodt)/(365.25/12)

qaly$delfinct2 <- qaly$delfinct
qaly$delfinct2[!is.na(qaly$delbmt)]<-pmax(qaly$delfinct[!is.na(qaly$delbmt)],qaly$delbmt[!is.na(qaly$delbmt)]) #add ,qaly$delbmt1[!is.na(qaly$delbmt1)],qaly$delbmt2[!is.na(qaly$delbmt2)]
#It takes in account the complication ecountered after the transplant
#finct
qaly$finct2 <- qaly$finct
qaly$finct2[!is.na(qaly$delbmt)]<-1
```

### Compute the survival curves for each arm

```{r}
library(survival)

# Arm A
ct_A  <- survfit(Surv(delfinct,finct)~1,data=qaly,subset = (R1 == "Intensive arm (A)")) # ct : Durée du traitement
ct2_A  <- survfit(Surv(delfinct2,finct2)~1,data=qaly,subset = (R1 == "Intensive arm (A)")) #Durée du traitement avec complications
sv_A  <- survfit(Surv(suivi,as.numeric(as.character(dc)))~1,data=qaly,subset = (R1 == "Intensive arm (A)")) # Durée de survie : Temps avant décès
efs_A <- survfit(Surv(delpfs,as.numeric(as.character(pfs)))~1, data=qaly,subset = (R1 == "Intensive arm (A)")) # Durée de survie sans progression : Temps avant rechute 

# Arm B
ct_B  <- survfit(Surv(delfinct,finct)~1,data=qaly,subset = (R1 == "Light arm (B)"))
ct2_B  <- survfit(Surv(delfinct2,finct2)~1,data=qaly,subset = (R1 == "Light arm (B)"))
sv_B  <- survfit(Surv(suivi,as.numeric(as.character(dc)))~1,data=qaly,subset = (R1 == "Light arm (B)"))
efs_B <- survfit(Surv(delpfs,as.numeric(as.character(pfs)))~1, data=qaly,subset = (R1 == "Light arm (B)"))


```

## Plot the survival curves for each arm

```{r}
ct<- survfit(Surv(delfinct,finct)~R1,data=qaly)
plot(ct)

survdiff(Surv(delfinct,finct)~R1,data=qaly)
```

### Bras A

```{r }
#fig.width=6, fig.height=5.5 => use later for website

fit1<-list(CT = ct_A, CT2=ct2_A,SV=sv_A, EFS=efs_A)
library(survminer)
library(gridExtra)
colors <- c("#A31621", "#053C5E", "#F3A712", "#1F7A8C", "#AFB3F7")

t<-ggsurvplot_combine(fit1,
          risk.table = TRUE,                  # Add risk table
   xlab = "Time in days",   # customize X axis label.
   ggtheme = theme_light(), # customize plot and risk table with a therme.
 risk.table.y.text.col = T, # colour risk table text annotations.
  risk.table.y.text = FALSE,
  legend.labs = c("CT","CT2","SV","EFS"))

sv_plot_A <- ggsurvplot(sv_A, risk.table = TRUE,
                      ggtheme = theme_light(),
                      # tables.theme = theme(
                      #   axis.text.x = element_blank(),  # Hide x-axis text
                      #   axis.ticks.x = element_blank(), # Hide x-axis ticks
                      #   axis.title.x = element_blank()  # Optionally, hide the x-axis title as well
                      # ),
                      risk.table.y.text.col = TRUE,
                      risk.table.y.text = FALSE,
                      palette = colors[2])  

library(dplyr)
library(gt)
library(gtsummary)
library(ks)
library(tidyr)
library(survival)
library(ggplot2)
library(ggsurvfit)


df<-t$plot$data
surv_A<-df %>% mutate(strata = sub("x=", "", strata)) %>%
  group_by(strata) %>%
  summarise(time = c(time - 0.001, time),
            surv = c(1, head(surv, -1), surv),
            .groups = "drop") %>%
  arrange(time) %>%
  pivot_wider(names_from = "strata", values_from = "surv") %>%
  fill(1:5, .direction = "downup") %>%
  ggplot(aes(time, CT)) +
  geom_step(aes(linetype = "CT")) +
  geom_ribbon(aes(ymin = 0, ymax = CT, fill = "TOX1"),alpha=0.5)+
  geom_step(aes(y = CT2, linetype = "CT2"),linewidth=0.9, colour="#0077b6") +
  geom_ribbon(aes(ymin = CT, ymax = CT2, fill = "TOX2"),alpha=0.5) +
  geom_step(aes(y = EFS,linetype = "EFS"),linewidth=0.9, colour="#48cae4") +
  geom_ribbon(aes(ymin = CT2, ymax = EFS, fill = "TWiST"),alpha=0.5)+
  geom_step(aes(y = SV,linetype = "SV"),linewidth=0.9, colour="#caf0f8")+
  geom_ribbon(aes(ymin = EFS, ymax = SV, fill = "REL"),alpha=0.5)+
  scale_fill_manual(values = c("TOX1" = "#03045e", "TOX2" = "#0077b6", "TWiST" = "#48cae4", "REL" = "#caf0f8")) +
  labs(x = "Time", y = "Survival Probability", linetype = "Duration", fill = "Events") +
  theme_minimal() +
  theme(legend.position = "right")

combined_plot <- grid.arrange(surv_A, sv_plot_A$table, ncol = 1,heights = c(6, 2))

```

#### Partition 1

```{r}
library(survminer)
library(survival)
library(gridExtra) # or library(patchwork)

# Assuming ct, sv, and efs are survival objects
fit1 <- list(CT = ct_A, SV = sv_A, EFS = efs_A)

# custom color palette for CT, SV, EFS
colors <- c("#A31621", "#053C5E", "#F3A712", "#1F7A8C", "#AFB3F7")

# Step 1: Generate the Combined Survival Plot without a risk table
surv1_A <- ggsurvplot_combine(fit1,
                        risk.table = FALSE,  # Disable risk table here
                        xlab = "Time in days",
                        ggtheme = theme_light(),
                        legend.labs = c("CT","SV","EFS"),
                        palette=colors,
                        title="Bras A")

# Step 2: Generate a Separate Risk Table for "SV"
# Note: This assumes 'sv' is a fit object from survival analysis.
# If 'sv' is not directly usable, you might need to recreate the survival analysis for SV.
sv_plot_A <- ggsurvplot(sv_A, risk.table = TRUE,
                      ggtheme = theme_light(),
                      # tables.theme = theme(
                      #   axis.text.x = element_blank(),  # Hide x-axis text
                      #   axis.ticks.x = element_blank(), # Hide x-axis ticks
                      #   axis.title.x = element_blank()  # Optionally, hide the x-axis title as well
                      # ),
                      risk.table.y.text.col = TRUE,
                      risk.table.y.text = FALSE,
                      palette = colors[2])  # Adjust 'colors[2]' as per your color setup


# Step 3: Combine the Plot and the Risk Table Manually
# Option 1: Using gridExtra
combined_plot <- grid.arrange(surv1_A$plot, sv_plot_A$table, ncol = 1,heights = c(6, 2))

# Or Option 2: Using patchwork (Uncomment to use)
# combined_plot <- g$plot / sv_plot$table

# Print or save the combined plot
print(combined_plot)

```

#### Partition 2

```{r}
library(survminer)
library(survival)
library(gridExtra) # or library(patchwork)

# Assuming ct, sv, and efs are survival objects
fit2 <- list(CT = ct_A, SV = sv_A, EFS = efs_A, CT2 = ct2_A)

# custom color palette for CT, SV, EFS
colors <- c("#A31621", "#053C5E", "#F3A712", "#1F7A8C", "#AFB3F7")

# Step 1: Generate the Combined Survival Plot without a risk table
surv2_A <- ggsurvplot_combine(fit2,
                        risk.table = FALSE,  # Disable risk table here
                        xlab = "Time in days",
                        ggtheme = theme_light(),
                        legend.labs = c("CT","SV","EFS","CT2"),
                        palette=colors,
                        title="Bras A")



# Step 3: Combine the Plot and the Risk Table Manually
# Option 1: Using gridExtra
combined_plot <- grid.arrange(surv2_A$plot, sv_plot_A$table, ncol = 1,heights = c(6, 2))

# Print or save the combined plot
print(combined_plot)

```

```{r fig.width=6, fig.height=5.5}
# fit2<-list(CT = ct, CT2 = ct2, SV=sv, EFS=efs)
# library(survminer)
# t<-ggsurvplot_combine(fit,
#           risk.table = TRUE,                  # Add risk table
#    xlab = "Time in days",   # customize X axis label.
#    ggtheme = theme_light(), # customize plot and risk table with a therme.
#  risk.table.y.text.col = T, # colour risk table text annotations.
#   risk.table.y.text = FALSE,
#   legend.labs = c("CT", "CT2","SV","EFS"))
# t
```

### Bras B

#### Partition 1

```{r}
library(survminer)
library(survival)
library(gridExtra) # or library(patchwork)

# Assuming ct, sv, and efs are survival objects
fit1 <- list(CT = ct_B, SV = sv_B, EFS = efs_B)

# custom color palette for CT, SV, EFS
colors <- c("#A31621", "#053C5E", "#F3A712", "#1F7A8C", "#AFB3F7")

# Step 1: Generate the Combined Survival Plot without a risk table
surv1_B <- ggsurvplot_combine(fit1,
                        risk.table = FALSE,  # Disable risk table here
                        xlab = "Time in days",
                        ggtheme = theme_light(),
                        legend.labs = c("CT","SV","EFS"),
                        palette=colors,
                        title="Bras B")

# Step 2: Generate a Separate Risk Table for "SV"
# Note: This assumes 'sv' is a fit object from survival analysis.
# If 'sv' is not directly usable, you might need to recreate the survival analysis for SV.
sv_plot_B <- ggsurvplot(sv_B, risk.table = TRUE,
                      ggtheme = theme_light(),
                      # tables.theme = theme(
                      #   axis.text.x = element_blank(),  # Hide x-axis text
                      #   axis.ticks.x = element_blank(), # Hide x-axis ticks
                      #   axis.title.x = element_blank()  # Optionally, hide the x-axis title as well
                      # ),
                      risk.table.y.text.col = TRUE,
                      risk.table.y.text = FALSE,
                      palette = colors[2])  # Adjust 'colors[2]' as per your color setup


# Step 3: Combine the Plot and the Risk Table Manually
# Option 1: Using gridExtra
combined_plot <- grid.arrange(surv1_B$plot, sv_plot_B$table, ncol = 1,heights = c(6, 2))

# Or Option 2: Using patchwork (Uncomment to use)
# combined_plot <- g$plot / sv_plot$table

# Print or save the combined plot
print(combined_plot)

```

#### Partition 2

```{r}
library(survminer)
library(survival)
library(gridExtra) # or library(patchwork)

# Assuming ct, sv, and efs are survival objects
fit2 <- list(CT = ct_B, SV = sv_B, EFS = efs_B, CT2 = ct2_B)

# custom color palette for CT, SV, EFS
colors <- c("#A31621", "#053C5E", "#F3A712", "#1F7A8C", "#AFB3F7")

# Step 1: Generate the Combined Survival Plot without a risk table
surv2_B <- ggsurvplot_combine(fit2,
                        risk.table = FALSE,  # Disable risk table here
                        xlab = "Time in days",
                        ggtheme = theme_light(),
                        legend.labs = c("CT","SV","EFS","CT2"),
                        palette=colors,
                        title="Bras B")



# Step 3: Combine the Plot and the Risk Table Manually
# Option 1: Using gridExtra
combined_plot <- grid.arrange(surv2_B$plot, sv_plot_B$table, ncol = 1,heights = c(6, 2))

# Print or save the combined plot
print(combined_plot)

```

# RMST

## Computing rmst for each arm

```{r rmst_computing}
# Charger les packages nécessaires
library(survival)
library(survRM2) # Assurez-vous que le package rmst2 est installé pour accéder à cette fonction
library(boot)

### 0 = Int arm A, 1 = Light arm B
t_censure <- 60#min(64.3285421,60.9774127) # 20% de censure

# For ct_rmst
ct_rmst<-rmst2(qaly$delfinct, qaly$finct, as.factor(as.numeric(qaly$R1)-1), covariates = NULL, alpha = 0.05)

ct_rmstB<-ct_rmst$RMST.arm1$rmst[1]
ct_rmstA<-ct_rmst$RMST.arm0$rmst[1]

# For ct2_rmst
ct2_rmst<-rmst2(qaly$delfinct2, qaly$finct2, as.factor(as.numeric(qaly$R1)-1), covariates = NULL, alpha = 0.05)
ct2_rmstB <- ct2_rmst$RMST.arm1$rmst[1]  # Assuming arm1 corresponds to arm B
ct2_rmstA <- ct2_rmst$RMST.arm0$rmst[1]  # Assuming arm0 corresponds to arm A

# For sv_rmst
sv_rmst<-rmst2(qaly$suivi, as.numeric(as.character(qaly$dc)), as.factor(as.numeric(qaly$R1)-1), tau = t_censure, covariates = NULL, alpha = 0.05)
sv_rmstB <- sv_rmst$RMST.arm1$rmst[1]
sv_rmstA <- sv_rmst$RMST.arm0$rmst[1]

# For efs_rmst
efs_rmst<-rmst2(qaly$delpfs, as.numeric(as.character(qaly$pfs)), as.factor(as.numeric(qaly$R1)-1), tau = t_censure, covariates = NULL, alpha = 0.05)
efs_rmstB <- efs_rmst$RMST.arm1$rmst[1]
efs_rmstA <- efs_rmst$RMST.arm0$rmst[1]

# Calculer TOX, TWiST, et REL en utilisant les RMST calculés
tox1_A = ct_rmstA
tox2_A = ct2_rmstA
twist1_A = efs_rmstA - ct_rmstA
twist2_A= efs_rmstA - ct2_rmstA
rel_A = sv_rmstA - efs_rmstA


# Calculer TOX, TWiST, et REL en utilisant les RMST calculés
tox1_B = ct_rmstB
tox2_B = ct2_rmstB
twist1_B = efs_rmstB - ct_rmstB
twist2_B= efs_rmstB - ct2_rmstB
rel_B = sv_rmstB - efs_rmstB
```

#### Boostrapping

##### TOX/TWISt/REL & their differences between group

```{r}
# Fonction pour calculer les RMST sur un échantillon bootstrapé

calculate_rmst <- function(data, indices, uTWiST, uTOX, uREL, t_censure) {
  sampled_data <- data[indices, ]
  
  # Calculer les RMST pour chaque bras et chaque étape
  ct_rmst <- rmst2(sampled_data$delfinct, sampled_data$finct, as.factor(as.numeric(sampled_data$R1)-1), covariates = NULL, alpha = 0.05)
  ct_rmstB <- ct_rmst$RMST.arm1$rmst[1]
  ct_rmstA <- ct_rmst$RMST.arm0$rmst[1]
  
  ct2_rmst <- rmst2(sampled_data$delfinct2, sampled_data$finct2, as.factor(as.numeric(sampled_data$R1)-1), covariates = NULL, alpha = 0.05)
  ct2_rmstB <- ct2_rmst$RMST.arm1$rmst[1]
  ct2_rmstA <- ct2_rmst$RMST.arm0$rmst[1]
  
  sv_rmst <- rmst2(sampled_data$suivi, as.numeric(as.character(sampled_data$dc)), as.factor(as.numeric(sampled_data$R1)-1), tau = t_censure, covariates = NULL, alpha = 0.05)
  sv_rmstB <- sv_rmst$RMST.arm1$rmst[1]
  sv_rmstA <- sv_rmst$RMST.arm0$rmst[1]
  
  efs_rmst <- rmst2(sampled_data$delpfs, as.numeric(as.character(sampled_data$pfs)), as.factor(as.numeric(sampled_data$R1)-1), tau = t_censure, covariates = NULL, alpha = 0.05)
  efs_rmstB <- efs_rmst$RMST.arm1$rmst[1]
  efs_rmstA <- efs_rmst$RMST.arm0$rmst[1]
  
  # Calculer les tox, twists et rels pour chaque bras et chaque étape
  tox1_A <- ct_rmstA
  tox2_A <- ct2_rmstA
  twist1_A <- efs_rmstA - ct_rmstA
  twist2_A <- efs_rmstA - ct2_rmstA
  rel_A <- sv_rmstA - efs_rmstA
  
  tox1_B <- ct_rmstB
  tox2_B <- ct2_rmstB
  twist1_B <- efs_rmstB - ct_rmstB
  twist2_B <- efs_rmstB - ct2_rmstB
  rel_B <- sv_rmstB - efs_rmstB
  
  # Calculer les différences entre les bras
  tox1_diff <- tox1_A - tox1_B
  tox2_diff <- tox2_A - tox2_B
  twist1_diff <- twist1_A - twist1_B
  twist2_diff <- twist2_A - twist2_B
  rel_diff <- rel_A - rel_B
  
  # Calculer QTWiST pour chaque partition
  q_twist1_A <- (uTOX * tox1_A) + (uTWiST * twist1_A) + (uREL * rel_A)
  q_twist1_B <- (uTOX * tox1_B) + (uTWiST * twist1_B) + (uREL * rel_B)
  q_twist1_diff <- q_twist1_A - q_twist1_B
  
  q_twist2_A <- (uTOX * (tox1_A + tox2_A)) + (uTWiST * (twist1_A + twist2_A)) + (uREL * rel_A)
  q_twist2_B <- (uTOX * (tox1_B + tox2_B)) + (uTWiST * (twist1_B + twist2_B)) + (uREL * rel_A)
  q_twist2_diff <- q_twist2_A - q_twist2_B
  
  # Retourner les résultats
  return(c("TOX1 A" = tox1_A, "TOX2 A" = tox2_A, "TWiST1 A" = twist1_A, "TWiST2 A" = twist2_A, "REL A" = rel_A, 
            "TOX1 B" = tox1_B, "TOX2 B" = tox2_B, "TWiST1 B" = twist1_B, "TWiST2 B" = twist2_B, "REL B" = rel_B, 
            "TOX1diff" = tox1_diff, "TOX2 diff" = tox2_diff, "TWiST1 diff" = twist1_diff, "twist2_diff" = twist2_diff, 
            "REL diff" = rel_diff,"q_TWiST1 A" = q_twist1_A, "q_TWiST1 B" = q_twist1_B, "q_TWiST1 diff" = q_twist1_diff, 
            "q_TWiST2 A" = q_twist2_A, "q_TWiST2 B" = q_twist2_B, "q_TWiST2 diff" = q_twist2_diff))}

# Appliquer le bootstrap sur le dataset 'qaly'
t_censure <- min(64.3285421, 60.9774127) # 20% de censure
qaly_cens<-qaly %>% select(delfinct, finct, delfinct2, finct2, suivi, dc, delpfs, pfs, R1)
bootstrap_results1 <- censboot(qaly_cens, calculate_rmst, R = 1000, uTWiST = 1, uTOX = 0.5, uREL = 0.5, t_censure = t_censure)

boot_summary<-summary(bootstrap_results1) %>% as.data.frame() 
rownames(boot_summary) <- names(bootstrap_results1$t0)
```

### Threshold analysis for Q-TWIST diff with computed var-cov

```{r boot1}
resultsboot<-as.data.frame(bootstrap_results1$t) %>%
  select("V1", "V3", "V5", "V6", "V8", "V10","V11","V13","V15") %>%
  rename(toxA = "V1", twistA = "V3", relA = "V5", toxB = "V6", twistB = "V8", relB = "V10",toxDiff="V11", twistDiff="V13", relDiff="V15")

# Attention, nous ne trouvons pas les mêmes var covariances pour les différences de qtwist
var(resultsboot$toxDiff)
var(resultsboot$twistDiff)
var(resultsboot$relDiff)

cov(resultsboot$toxDiff, resultsboot$twistDiff)
cov(resultsboot$toxDiff, resultsboot$relDiff)
cov(resultsboot$twistDiff, resultsboot$relDiff)
```

```{r}
variance_QTwist <- function(U_TOX, U_REL, Var_TOX, Var_TWIST, Var_REL, Cov_TOX_TWIST, Cov_TOX_REL, Cov_TWIST_REL) {
  variance <- (U_TOX^2) * Var_TOX + Var_TWIST + (U_REL^2) * Var_REL
  variance <- variance + 2* (U_TOX * Cov_TOX_TWIST + U_TOX * U_REL * Cov_TOX_REL + U_REL * Cov_TWIST_REL)
  return(variance)
}

# Matrice de variance-covariance des estimateurs bootstrappés

# Var_TOX <- var(resultsdiff$toxDiff)
# Var_TWIST <- var(resultsdiff$twistDiff)
# Var_REL <- var(resultsdiff$relDiff)
# Cov_TOX_TWIST <- cov(resultsdiff$toxDiff, resultsdiff$twistDiff)
# Cov_TOX_REL <- cov(resultsdiff$toxDiff, resultsdiff$relDiff)
# Cov_TWIST_REL <- cov(resultsdiff$twistDiff, resultsdiff$relDiff)

Var_TOX <- 0.175**2
Var_TWIST <- 3.73**2
Var_REL <- 2.06**2
Cov_TOX_TWIST <- 2.84e-2 
Cov_TOX_REL <- -1.82e-2
Cov_TWIST_REL <- -0.55


# QTWiST

results <- data.frame(uTOX=numeric(), uREL=numeric(), QTWiST1_Diff=numeric(), Lower=numeric(), Upper=numeric())
uTWiST=1
for (uTOX in seq(0, 1, by=0.25)) {
  for (uREL in seq(0, 1, by=0.25)) {
    
  # Calculer les RMST pour chaque bras et chaque étape
  ct_rmst <- rmst2(qaly$delfinct, qaly$finct, as.factor(as.numeric(qaly$R1)-1), covariates = NULL, alpha = 0.05)
  ct_rmstB <- ct_rmst$RMST.arm1$rmst[1]
  ct_rmstA <- ct_rmst$RMST.arm0$rmst[1]
  
  # ct2_rmst <- rmst2(qaly$delfinct2, qaly$finct2, as.factor(as.numeric(qaly$R1)-1), covariates = NULL, alpha = 0.05)
  # ct2_rmstB <- ct2_rmst$RMST.arm1$rmst[1]
  # ct2_rmstA <- ct2_rmst$RMST.arm0$rmst[1]
  
  sv_rmst <- rmst2(qaly$suivi, as.numeric(as.character(qaly$dc)), as.factor(as.numeric(qaly$R1)-1), tau = t_censure, covariates = NULL, alpha = 0.05)
  sv_rmstB <- sv_rmst$RMST.arm1$rmst[1]
  sv_rmstA <- sv_rmst$RMST.arm0$rmst[1]
  
  efs_rmst <- rmst2(qaly$delpfs, as.numeric(as.character(qaly$pfs)), as.factor(as.numeric(qaly$R1)-1), tau = t_censure, covariates = NULL, alpha = 0.05)
  efs_rmstB <- efs_rmst$RMST.arm1$rmst[1]
  efs_rmstA <- efs_rmst$RMST.arm0$rmst[1]
  
  # Calculer les tox, twists et rels pour chaque bras et chaque étape
  tox1_A <- ct_rmstA
  twist1_A <- efs_rmstA - ct_rmstA
  rel_A <- sv_rmstA - efs_rmstA
  
  tox1_B <- ct_rmstB
  twist1_B <- efs_rmstB - ct_rmstB
  rel_B <- sv_rmstB - efs_rmstB
  
  # Calculer les différences entre les bras
  tox1_diff <- tox1_A - tox1_B
  twist1_diff <- twist1_A - twist1_B
  rel_diff <- rel_A - rel_B
  
  # Calculer QTWiST pour chaque partition
  q_twist1_A <- (uTOX * tox1_A) + (uTWiST * twist1_A) + (uREL * rel_A)
  q_twist1_B <- (uTOX * tox1_B) + (uTWiST * twist1_B) + (uREL * rel_B)
  q_twist1_diff <- q_twist1_A - q_twist1_B
  
  variance_qTwist <- variance_QTwist(uTOX, uREL, Var_TOX, Var_TWIST, Var_REL, Cov_TOX_TWIST, Cov_TOX_REL, Cov_TWIST_REL)
  ic_qTwist_inf <- q_twist1_diff - 1.96*sqrt(variance_qTwist)
  ic_qTwist_sup<-q_twist1_diff + 1.96*sqrt(variance_qTwist)
  
      # Ajouter les résultats dans le dataframe
  results <- rbind(results, data.frame(
      uTOX=uTOX, 
      uREL=uREL, 
      QTWiST1_Diff=q_twist1_diff, 
      Lower=ic_qTwist_inf, # Lower CI
      Upper=ic_qTwist_sup  # Upper CI
    ))
  }
}
```

```{r}
# Filtrer les résultats où l'intervalle de confiance contient 0
diff_null <- results %>% filter(Lower <= 0, Upper >= 0) 

# Tracer le graphique en utilisant uTOX sur l'axe x et QTWiST1_Diff sur l'axe y, et uREL en tant que couleur
plot(diff_null$uTOX, diff_null$QTWiST1_Diff, pch = 19, col = "red", xlab = "uTOX", ylab = "QTWiST1_Diff", main = "Confidence interval contains 0")
# Ajouter uREL comme troisième axe
points(diff_null$QTWiST1_Diff, diff_null$uTOX, pch = 19, col = "blue")
# Légende
legend("bottomright", legend = c("QTWiST1_Diff", "uREL"), col = c("red", "blue"), pch = 19)


# library(ggplot2)
# # Créer le graphique
# ggplot(diff_null, aes(x = uTOX, y = uREL)) +
#   geom_point() + 
#   scale_x_continuous(name = "Utility coefficient after relapse (μ_REL)", limits = c(0, 1)) +
#   scale_y_continuous(name = "Utility coefficient for toxicity (μ_TOX)", limits = c(0, 1)) +
#   geom_abline(diffQTWiST1_Diff, linetype = "dashed")
```

### Threshold analysis for Q-TWIST diff with bootstrapp var-cov

```{r}
delta_qtwist <- function(data, indices, uTWiST, uTOX, uREL, t_censure) {
  sampled_data <- data[indices, ]
  
  # Calculer les RMST pour chaque bras et chaque étape
  ct_rmst <- rmst2(sampled_data$delfinct, sampled_data$finct, as.factor(as.numeric(sampled_data$R1)-1), covariates = NULL, alpha = 0.05)
  ct_rmstB <- ct_rmst$RMST.arm1$rmst[1]
  ct_rmstA <- ct_rmst$RMST.arm0$rmst[1]
  
  # ct2_rmst <- rmst2(sampled_data$delfinct2, sampled_data$finct2, as.factor(as.numeric(sampled_data$R1)-1), covariates = NULL, alpha = 0.05)
  # ct2_rmstB <- ct2_rmst$RMST.arm1$rmst[1]
  # ct2_rmstA <- ct2_rmst$RMST.arm0$rmst[1]
  
  sv_rmst <- rmst2(sampled_data$suivi, as.numeric(as.character(sampled_data$dc)), as.factor(as.numeric(sampled_data$R1)-1), tau = t_censure, covariates = NULL, alpha = 0.05)
  sv_rmstB <- sv_rmst$RMST.arm1$rmst[1]
  sv_rmstA <- sv_rmst$RMST.arm0$rmst[1]
  
  efs_rmst <- rmst2(sampled_data$delpfs, as.numeric(as.character(sampled_data$pfs)), as.factor(as.numeric(sampled_data$R1)-1), tau = t_censure, covariates = NULL, alpha = 0.05)
  efs_rmstB <- efs_rmst$RMST.arm1$rmst[1]
  efs_rmstA <- efs_rmst$RMST.arm0$rmst[1]
  
  # Calculer les tox, twists et rels pour chaque bras et chaque étape
  tox1_A <- ct_rmstA
  twist1_A <- efs_rmstA - ct_rmstA
  rel_A <- sv_rmstA - efs_rmstA
  
  tox1_B <- ct_rmstB
  twist1_B <- efs_rmstB - ct_rmstB
  rel_B <- sv_rmstB - efs_rmstB
  
  # Calculer les différences entre les bras
  tox1_diff <- tox1_A - tox1_B
  twist1_diff <- twist1_A - twist1_B
  rel_diff <- rel_A - rel_B
  
  # Calculer QTWiST pour chaque partition
  q_twist1_A <- (uTOX * tox1_A) + (uTWiST * twist1_A) + (uREL * rel_A)
  q_twist1_B <- (uTOX * tox1_B) + (uTWiST * twist1_B) + (uREL * rel_B)
  q_twist1_diff <- q_twist1_A - q_twist1_B
  
  
  # Retourner les résultats
  return("q_TWiST1 diff" = q_twist1_diff)}


# delta_qtwist_boot <- censboot(qaly_cens, delta_qtwist, R = 1000, uTWiST = 1, uTOX = 0.5, uREL = 0.5, t_censure = t_censure)
# boot.ci(delta_qtwist_boot,type="norm")$normal
library(boot)
# QTWiST
results1 <- data.frame(uTOX=numeric(), uREL=numeric(), QTWiST1_Diff=numeric(), Lower=numeric(), Upper=numeric())

for (uTOX in seq(0, 1, by=0.25)) {
  for (uREL in seq(0, 1, by=0.25)) {
    # Bootstrap analysis
    delta_qtwist_boot <- censboot(qaly_cens, delta_qtwist, R = 1000, uTWiST = uTWiST, uTOX = uTOX, uREL = uREL, t_censure = t_censure)
    boot_results <- boot.ci(delta_qtwist_boot, type="norm")
    boot_results$normal[2]
    # Ajouter les résultats dans le dataframe
results1 <- rbind(results1, data.frame(
      uTOX=uTOX, 
      uREL=uREL, 
      QTWiST1_Diff=q_twist1_diff, 
      Lower=boot_results$normal[2], # Lower CI
      Upper=boot_results$normal[3]  # Upper CI
))
    }
}

sum(!is.na(qaly$relapsdt))


```

## Export results in latex

```{r}
if (!require("xtable")) install.packages("xtable")
library(xtable)

rownames(results)
print(xtable(results), type = "latex", include.rownames = FALSE)
# # %>% 
#   as_gt()%>% 
#   gtsave("name.text")
```
